---
title: "How to use CSIimport"
author: "Bryan McCloskey"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{A guide to using CSIimport}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The `CSI` (Coastal Salinity Index) package is designed to import salinity data in a variety of formats, clean and interpolate missing data, calculate CSI and other similar metrics, and produce CSV and graphical outputs. The `CSI` is based on the `SPI`/`SPEI` (Standardized Precipitation Index/Standardized Precipitation-Evapotranspiration Index) package metrics. `CSI` is able to:

- Read data in 15-minute, 60-minute, daily, and irregular interval formats,
- Convert specific conductance to salinity, if necessary,
- Interpolate missing data using linear or spline interpolation,
- Calculate CSI values and salinity departures from normal,
- Produce CSV and graphical outputs.

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
